WrapITK: Enhanced languages support\\ for the Insight Toolkit

### 2006-04-18 article/Article.tex
some details in the article
darcs-hash:20060418140413-2fc9d-165bf780cd6b9e3db7d7fabb4a9e096f0e923d0d.gz

  \item \verb$darcs send$ to send by email the patches you have recorded with
\verb$darcs record$.
% TODO: which email adress ??

@@

ITK is a great library, with the drawback to be nearly unusable for prototyping,
and to have a poor support for other languages than C++. WrapITK address those
issue and finally give to ITK a quite good support for python. We hope that support
will soon be extended to tcl and java.

>>>>

  \item \verb$darcs send$ to send by email the patches you have recorded with
\verb$darcs record$. Please send your patches to the WrapITK bugtracker
(wrapitk-bugmaster@jouy.inra.fr\footnote{Note that you must have an account to
be able to send something to the bug tracker. Visit
\url{http://voxel.jouy.inra.fr/roundup/wrapitk/} to create one.}) so everyone
would be able to find it easily.

@@

ITK is a great library, with the drawback to be nearly unusable for prototyping,
and to have a poor support for other languages than C++. WrapITK address those
issue and finally give to ITK a good support for python. Java and Tcl, while
not as much tweaked than python part, also take benefit of the higher number of
wrapped classes, and of the increase of consistency in available types and names
